The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-26 dit-paper_ieee.tex
explained system modification for coprime n_i

	\subsection{Solving the modular system}
		A sketch of the construction algorithm to compute $t_d$ can be found in
		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
		modular inverse of $x$ in the naturals modulo $y$). In this paper we
		concentrate on the latter part of the algorithm (after the modifications to
		correct non-coprime periods, readers interested in the details of these
		modifications should refer to \cite{knuth1969art}).
		\begin{algorithm}
			\caption{Gauss's CRP Algorithm}
			\label{alg:algoCRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
				\REQUIRE $\forall \tau_i \in \tau : x_i = a_i+O_i$
				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE Modify the $n_i$ and $x_i$ by prime decomposition so \\ that the
				$n_i$ become pairwise coprime

				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
					\STATE $e_i \leftarrow Mj \cdot invMj$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{x_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}
		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks, and resolving exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances.

>>>>

	\subsection{Solving the modular system}
		A sketch of the construction algorithm to compute $t_d$ can be found in
		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
		modular inverse of $x$ in the naturals modulo $y$). The congruences must
		first be modified in order to obtain pairwise coprime moduli. Each $n_i$
		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$.
		Each original constraint $t_d \equiv x_i \; (mod \; n_i)$ is replaced by the
		equivalent set
		\begin{equation*}
			\begin{split}
				t_d \equiv x_i 	& \; (mod \; p^{k_1}_1) \\
				t_d \equiv x_i 	& \; (mod \; p^{k_2}_2) \\
								& \vdots \\
				t_d \equiv x_i 	& \; (mod \; p^{k_m}_m) \\
			\end{split}
		\end{equation*}
		This operation might create duplicate constraints, which are removed. As shown
		in \cite{knuth1969art}, the resulting system can be solved using
		Algorithm~\ref{alg:algoCRP}.

		\begin{algorithm}
			\caption{Gauss's CRP Algorithm}
			\label{alg:algoCRP}
			\begin{algorithmic}[1]
				\REQUIRE $H$ is the hyperperiod of the system
				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
					\STATE $e_i \leftarrow Mj \cdot invMj$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{x_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}

		%TODO change algo 2 with respect to explanation of coprime n_i

		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks, and resolving exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances.
